---
title: "Kagumba Community Based Organization - The CBO"
author: "Wyclife Agumba Oluoch"
date: "`r Sys.time()`"
categories: ["R"]
tags: ["R Markdown", "plot", "regression"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE)
```

# Background

Kagumba Community Based Organization, here under termed 'The CBO', is a group that brings together descendants of the late great Agumba Ochogo of Kano Katolo of Kisumu County in Kenya.  The CBO was formed on **5th December 2021** in order to help boost the economy and livelihood of the members. It is largely led by youths **(age <= 35 years)** and women whose majority are widows. 

# Objectives of The CBO

i.	To improve livelihood of members and the community by establishing and running small and medium scale projects.

ii.	To improve inclusion of youths, young girls, and women in both leadership and membership of The CBO for their individual and communal empowerment.

iii.	To participate in environmental conservation strategies that ensure ecosystem protection and conservation of nature within the community. 

iv.	To act as knowledge-sharing hub for members and the community at large on projects that can lift the community from abject poverty.

<center>**Vision**</center>

_To be a vibrant and self-reliant community based organization that lifts livelihood of members’ welfare and environmental concerns with dignity and integrity._

<center>**Mission**</center>

_A professional community based organization that generates skills and development-based projects and disseminates the same to Kenyan youths, young girls, and women as well as across the globe to ensure self-reliance and sustainability in livelihood improvement._

You can embed an R code chunk like this:

```{r echo=FALSE}
library(ggplot2)
ggplot(Orange, aes(x = age, 
                   y = circumference, 
                   color = Tree)) +
  geom_point() +
  geom_line() +
  guides(color = 'none') +
  theme_bw()
```



# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
